The GitHub Open Source Development Process \author{Kevin Peterson\\ Department of Information Technology\\ Clinical Informatics Support Systems\\ Mayo Clinic\\ 200 1st Street\\ Rochester, MN 55905\\ \small \texttt{peterson.kevin@mayo.edu} }

### 2013-03-19 paper/main.tex
Fixed some typos.

\begin{abstract}
Open Source Software (OSS) has produced many successful projects. The development process by which these projects are produced is generally unstructured compared to commercial software -- but a definite pattern does arrive, and is no less a pattern. GitHub, a popular OSS code hosting website, and Git, the site's SCM of choice, may have the potential to fundamentally change ths process.\\
By analyzing a subset of GitHub repositories, this report will show how GitHub has influenced some very intrinsic aspects of traditional OSS develoment, such as developer hierarchies and issue close velicity. We find that many of the traditional aspects of OSS development remain, such most project developlment is done by a small group of core developers. Others assumptions about project hierarchy, such as a large number of Issue Reporters compared to Committers, seems unsupported by the data.

@@

Because issue reporting is of low risk to the code base, but has potentially high value, it is a perfect way for large numbers of people to contribute. It is expected that the findings of the Apache Server project research will hold true for GitHub projects as well.\\

>>>>

\begin{abstract}
Open Source Software (OSS) has produced many successful projects. The development process by which these projects are produced is generally unstructured compared to commercial software -- but a definite pattern does arrive, and is no less a pattern. GitHub, a popular OSS code hosting website, and Git, the site's Source Code Management (SCM) tool of choice, may have the potential to fundamentally change ths process.\\
By analyzing a subset of GitHub repositories, this report will show how GitHub has influenced some very intrinsic aspects of traditional OSS develoment, such as developer hierarchies and issue close velicity. We find that many of the traditional aspects of OSS development remain, such most project developlment is done by a small group of core developers. Others assumptions about project hierarchy, such as a large number of Issue Reporters compared to Committers, seems unsupported by the data.

@@

Because issue reporting is of low risk to the code base, but has potentially high value, it is a perfect way for large numbers of people to contribute. It is expected that the findings of the Apache Server project research will hold true for GitHub projects as well.
